### 2014-06-26 5/applications.tex
auto

\section{Clustering SAR images using the consistent measures}
\label{sec:k_mle}

Given an area to be analyzed, 
  the question of whether it is homogeneous or not can be investigated using
the statistical hypothesis test described in chapter \ref{chap:sar}. 
If that is found to be the case, a clustering algorithm can then be applied to partition the area into smaller regions. 
Thus an image can be segmented into homogeneous areas by applying the process repeatedly.

@@

\begin{eqnarray*}
\ln[P(X^l | \mu )] 
	= \displaystyle{\sum^n_{i=1}{ \ln(P(x^l_i | \mu )) }} 
	= \displaystyle{\sum^n_{i=1}{ \ln \left[ \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} } \right] }} 
%	&=& n \ln \ln 2 +  \displaystyle{\sum^n_{i=1}{ \ln \left( 2^{x^l_i - \mu} \right) - \ln \left( e^{2^{ x^l_i -\mu }} \right) }} 
\end{eqnarray*}

The parameter $\mu$ which maximizes the likelihood is found by setting its derivatives to zero:
\begin{eqnarray*}
\displaystyle{ \frac{ \partial{ \ln[P( X^l | \mu )] }  }{\partial{ \mu }} }
	&=& 0 \\
\displaystyle{ \frac{ \partial }{\partial{ \mu }} \sum^n_{i=1}{ \ln( 2^{x^l_i - \mu}) - \ln( e^{2^{ x^l_i -\mu }} ) } }
	&=& 0 
%\displaystyle{ \frac{ \partial }{\partial{ \mu }} \sum^n_{i=1}{ \ln( 2^{x^l_i - \mu}) } }
%	&=& - n \cdot \ln2  \\
%\displaystyle{ \frac{ \partial }{\partial{ \mu }} \sum^n_{i=1}{ \ln( e^{2^{ x^l_i -\mu }} )i } }
%	&=& - \ln2 \cdot \sum^n_{i=1}{ 2^{ x^l_i -\mu } } \\
%	&=& - \ln2 \cdot \frac{ \sum^n_{i=1}{ 2^{ x^l_i } }}{2^\mu}  
\end{eqnarray*}

@@

PS: During the revision of this thesis, this work \cite{Nielsen_2012_ICASSP} is brough forward to the author's attention.
This work is quite similar and is published after the publication for the work presented in this thesis \cite{Le_2010_ACRS}.
It excels by providing a theoretical proof for its k-MLE procedure in the case of exponential mixtures.
Its drawback: it focuses only on the exponential distribution, which is just one special case of the work presented here.

\section{SAR Speckle filtering using the consistent measures}

@@

\begin{figure}[h!]
\centering
\subfloat[Intensity histogram]{
  \epsfxsize=6cm
  \epsfysize=6cm
  \epsffile{images/consistent_contrast_log_domain.made.eps}
\label{fig:consistent_contrast_log_domain}
  }
\caption{Consistent Distance Property and the f-MLE Estimations}
\end{figure}

@@

\begin{figure}[H]
\centering
	\subfloat[f-MLE (incl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.123}
	}
	\subfloat[f-MLE (incl): 456]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.345}
	} 
	\subfloat[f-MLE (excl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.123}
	}
	\subfloat[f-MLE (excl): 456]{          
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.345}
	}
\caption{Iteratively Improving in Distance Histograms}
\label{fig:plot_incl_distance_pdf_by_iterations}
\end{figure}

@@

\section{Evaluating SAR Speckle Filters using the consistent measures of distance}

@@

Let us consider the multi-look processing effect in the log-transformed domain. 
%Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
Hoekmen \cite{Hoekman_1991_TGRS} and Xie et. al. \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random 
variables as: 
\begin{equation*}
var(\hat{X}^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right).
\label{eqn:perf_index_theoretical}
\end{equation*}

%Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
Based on the Euler proof for the Basel problem, we have
%$\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
%Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
%\setlength{\mathindent}{1cm}  
\begin{align*}
&\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } &\\
\noindent \text{then: } \\ 
&var(Y^L) = \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) &\\
\noindent \text{Noting that: }  \\
&\frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i} &\\
\noindent \text{then: } \\
&\frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} &
\end{align*}

@@

\section{Evaluating POLSAR Speckle Filters using the consistent measures of distance}

@@

In the case of partial POLSAR, d=2, then
{\small
\begin{align*}
&  var_2 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1)     = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2 &\\
\noindent \text{Similar to the SAR case: } \\
&  1/L + 1/(L-1) < var_2 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) & \\
\noindent \text{Thus, approximately: } \\
& var_2 \left[ \ln |C_v| \right] = 2/(L-1) & \\
\noindent \text{Equivalently: } \\
& L = 2/var_2 \left[ \ln |C_v| \right] + 1 & \\
\end{align*}
}%
%Similar to the SAR case, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
%Thus an approximation can be made: $var_d \left[ \ln |C_v| \right] = 2/(L-1)$.
%Equivalently L can be estimated as:  $L = 2/var_d \left[ \ln |C_v| \right] + 1$

In the case of full POLSAR, d=3, then
{\small
\begin{align*}
&  var_3 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) + \psi^1(L-2)    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2  + \sum^{\infty}_{i=L-2}1/i^2 & \\
\noindent \text{Again: }  \\
& 1/L + 1/(L-1) + 1/(L-2) < var_3 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3) &\\
\noindent \text{As } L>3 \\
& var_3 \left[ \ln |C_v| \right] = 3/(L-1.5) &\\
\noindent \text{Or: }\\
& L = 3/var_3 \left[ \ln |C_v| \right] + 1.5 &
\end{align*}
}%

>>>>

\section{
  Clustering and filtering SAR images 
  \footnote{
During the revision of this thesis, Nielsen's work \cite{Nielsen_2012_ICASSP} is brought forward to the author's attention.
This work is quite similar and is published after the publication for the work presented in this thesis \cite{Le_2010_ACRS}.
It excels by providing a theoretical proof for its k-MLE procedure in the case of exponential mixtures.
Its drawback: it focuses only on the exponential distribution, which is just one special case of the work presented here.
  }
}
\label{sec:k_mle}

Given an area to be analyzed, 
  the question of whether it is homogeneous or not can be investigated using
the statistical hypothesis test described in Chapter \ref{chap:sar}. 
If that is found to be the case, a clustering algorithm can then be applied to partition the area into smaller regions. 
Thus an image can be segmented into homogeneous areas by applying the process repeatedly.

@@

\begin{eqnarray}
\ln[P(X^l | \mu )] 
	= \displaystyle{\sum^n_{i=1}{ \ln(P(x^l_i | \mu )) }} 
	= \displaystyle{\sum^n_{i=1}{ \ln \left[ \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} } \right] }} 
%	&=& n \ln \ln 2 +  \displaystyle{\sum^n_{i=1}{ \ln \left( 2^{x^l_i - \mu} \right) - \ln \left( e^{2^{ x^l_i -\mu }} \right) }} 
\end{eqnarray}

The parameter $\mu$ which maximizes the likelihood is found by setting its derivatives to zero:
\begin{eqnarray}
\displaystyle{ \frac{ \partial{ \ln[P( X^l | \mu )] }  }{\partial{ \mu }} }
	&=& 0 \\
\displaystyle{ \frac{ \partial }{\partial{ \mu }} \sum^n_{i=1}{ \ln( 2^{x^l_i - \mu}) - \ln( e^{2^{ x^l_i -\mu }} ) } }
	&=& 0 
%\displaystyle{ \frac{ \partial }{\partial{ \mu }} \sum^n_{i=1}{ \ln( 2^{x^l_i - \mu}) } }
%	&=& - n \cdot \ln2  \\
%\displaystyle{ \frac{ \partial }{\partial{ \mu }} \sum^n_{i=1}{ \ln( e^{2^{ x^l_i -\mu }} )i } }
%	&=& - \ln2 \cdot \sum^n_{i=1}{ 2^{ x^l_i -\mu } } \\
%	&=& - \ln2 \cdot \frac{ \sum^n_{i=1}{ 2^{ x^l_i } }}{2^\mu}  
\end{eqnarray}

@@

\section{SAR Speckle filtering using the consistent measures}
\label{sec:f_mle}

@@

\begin{figure}[h!]
\centering
%\subfloat[Intensity histogram]{
  \epsfxsize=6cm
  \epsfysize=6cm
  \epsffile{images/consistent_contrast_log_domain.made.eps}
%  }
\caption{Consistent Distance Property and the f-MLE Estimations}
\label{fig:consistent_contrast_log_domain}
\end{figure}

@@

\begin{figure}[H]
\centering
	\subfloat[f-MLE (incl): 123]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/incl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.123}
	}
	\subfloat[f-MLE (incl): 456]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/incl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.345}
	} \\ 
	\subfloat[f-MLE (excl): 123]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/excl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.123}
	}
	\subfloat[f-MLE (excl): 456]{          
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/excl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.345}
	}
\caption{Iteratively Improving in Distance Histograms}
\label{fig:plot_incl_distance_pdf_by_iterations}
\end{figure}

@@

\section{Evaluating SAR Speckle Filters using the consistent measures of distance}
\label{sec:sar_filters_evaluation}

@@

Let us consider the multi-look processing effect in the log-transformed domain. 
%Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
Hoekmen \cite{Hoekman_1991_TGRS} and Xie et. al. \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random 
variables as: 
\begin{equation}
var(\hat{X}^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right).
\label{eqn:perf_index_theoretical}
\end{equation}

%Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
Based on the Euler proof for the Basel problem, we have
%$\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
%Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
%\setlength{\mathindent}{1cm}  
\begin{align}
&\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } &\\
\noindent \text{then: } \\ 
&var(Y^L) = \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) &\\
\noindent \text{Noting that: }  \\
&\frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i} &\\
\noindent \text{then: } \\
&\frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} &
\end{align}

@@

\section{Evaluating POLSAR Speckle Filters using the consistent measures of distance}
\label{sec:polsar_speckle_filters_evaluation}

@@

In the case of partial POLSAR, d=2, then
{\small
\begin{align}
&  var_2 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1)     = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2 &\\
\noindent \text{Similar to the SAR case: } \\
&  1/L + 1/(L-1) < var_2 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) & \\
\noindent \text{Thus, approximately: } \\
& var_2 \left[ \ln |C_v| \right] = 2/(L-1) & \\
\noindent \text{Equivalently: } \\
& L = 2/var_2 \left[ \ln |C_v| \right] + 1 & \\
\end{align}
}%
%Similar to the SAR case, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
%Thus an approximation can be made: $var_d \left[ \ln |C_v| \right] = 2/(L-1)$.
%Equivalently L can be estimated as:  $L = 2/var_d \left[ \ln |C_v| \right] + 1$

In the case of full POLSAR, d=3, then
{\small
\begin{align}
&  var_3 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) + \psi^1(L-2)    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2  + \sum^{\infty}_{i=L-2}1/i^2 & \\
\noindent \text{Again: }  \\
& 1/L + 1/(L-1) + 1/(L-2) < var_3 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3) &\\
\noindent \text{As } L>3 \\
& var_3 \left[ \ln |C_v| \right] = 3/(L-1.5) &\\
\noindent \text{Or: }\\
& L = 3/var_3 \left[ \ln |C_v| \right] + 1.5 &
\end{align}
}%

### 2014-06-26 6/conclusional_discussion.tex
auto

Corresponding to the objectives outlined in Chapter 1,
  the following results have been obtained:
\begin{enumerate}
\item           Several scalar and highly representative statistical models
                for the multi-dimensional and inter-correlated POLSAR
                data have been proposed:
                \begin{enumerate}
                \item The determinant statistical model is established for the determinant of POLSAR covariance matrices (Section \ref{sec:polsar_heterosked_model_and_log_transform}),
                \item Several statistical models for different discrimination measures (namely: determinant-ratio, log-distance, dispersion and contrast) are derived together with its consistent property (Section \ref{sec:consistent_measures_distance_polsar}). %being modelled 
                \item The proposed models for POLSAR are also shown to include the traditional SAR statistical models (Section \ref{sec:sar_special_case_of_polsar}).
                \item \label{itm:polsar_validation} The proposed models are validated against practical real-life
                captured POLSAR data in Section \ref{sec:polsar_models_validation}.
                \end{enumerate}
\item                Homoskedastic statistical models for the
                heteroskedastic (POL)SAR data are derived. Specifically 
                \begin{enumerate}
                \item \label{itm:log_transform} The statistical model for POLSAR data are shown to be heteroskedastic in
                the original domain and logarithmic transformation
                converts this into a homoskedastic model (Sections \ref{sec:heteroskedastic_sar}, \ref{sec:homoskedastic_sar}, \ref{sec:polsar_heterosked_model_and_log_transform}).
                \item \label{itm:sar_measures_distance} Homoskedastic measures of distance for
                the multi dimensional POLSAR as well as for the one
                dimensional SAR data are derived (Sections \ref{sec:consistent_measures_distance_sar}, \ref{sec:consistent_measures_distance_polsar})
                \item \label{itm:sar_validation} These statistical models are validated against both
                practical SAR and POLSAR data (Sections: \ref{sec:sar_special_case_of_polsar}, \ref{sec:polsar_models_validation})
                \end{enumerate}
\item The beneficial applications of these
                statistical models have also been demonstrated. Specifically:
                \begin{enumerate}
                \item \label{itm:filter_vicious_circle} The consistent sense of variance
                is shown to help breaking the vicious cycle in the problem of SAR
                speckle filtering: with new statistical test for
                homogeneity and new speckle filters proposed (Section \ref{sec:k_mle}, \ref{sec:f_mle}).
                \item \label{itm:log_mse} Tconsistent sense of subtractive
                distance also helps in the problem of evaluating SAR
                speckle filters. Section \ref{sec:sar_filters_evaluation} proposes the use of the log-MSE to combine the
                evaluation of radiometric preservation and speckle
                suppression power in evaluating SAR speckle filters.
                \item \label{itm:extend_sar_to_polsar} Section \ref{sec:polsar_models_validation} demonstrates an example where the existing SAR
                processing technique of ENL estimation is extended towards POLSAR data.
                \end{enumerate}
\end{enumerate}

@@

The
                proposed models for POLSAR also bring forward an
                important benefits.
Since
                the models, especially those for discrimination
                measures, can be considered as the multidimensional
                extension of the models for SAR, it makes many existing
                SAR processing techniques extensible towards POLSAR
                data.
The POLSAR determinant ratio, for example, can be considered as
                the extension of the ubiquitous SAR intensity ratio.
This
                thesis also illustrates how the MSE evaluation
                criteria can also be extended from SAR to POLSAR.

From another angle, the theoretical models for POLSAR also offer several benefits.
The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics} \& \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
can be simulated as:
\begin{align*}
  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align*}
where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
As a by-product of this exact derivation, the current paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.

>>>>

Corresponding to the objectives outlined in Chapter 1,
  the following results have been obtained:
\begin{enumerate}
\item           Several scalar and highly representative statistical models
                for the multi-dimensional and inter-correlated POLSAR
                data have been proposed:
                \begin{enumerate}
                \item The determinant statistical model is established for the determinant of POLSAR covariance matrices (Section \ref{sec:polsar_heterosked_model_and_log_transform}),
                \item Several statistical models for different discrimination measures (namely: determinant-ratio, log-distance, dispersion and contrast) are derived together with its consistent property (Section \ref{sec:consistent_measures_distance_polsar}). %being modelled 
                \item The proposed models for POLSAR are also shown to include the traditional SAR statistical models (Section \ref{sec:sar_special_case_of_polsar}).
                \item \label{itm:polsar_validation} The proposed models are validated against practical real-life
                captured POLSAR data in Section \ref{sec:polsar_models_validation}.
                \end{enumerate}
\item                Homoskedastic statistical models for the
                heteroskedastic (POL)SAR data are derived. Specifically 
                \begin{enumerate}
                \item \label{itm:log_transform} The statistical model for POLSAR data are shown to be heteroskedastic in
                the original domain and logarithmic transformation
                converts this into a homoskedastic model (Sections: \ref{sec:heteroskedastic_sar}, \ref{sec:homoskedastic_sar}, \ref{sec:polsar_heterosked_model_and_log_transform}).
                \item \label{itm:sar_measures_distance} Homoskedastic measures of distance for
                the multi dimensional POLSAR as well as for the one
                dimensional SAR data are derived (Sections: \ref{sec:consistent_measures_distance_sar}, \ref{sec:consistent_measures_distance_polsar})
                \item \label{itm:sar_validation} These statistical models are validated against both
                practical SAR and POLSAR data (Sections: \ref{sec:sar_special_case_of_polsar}, \ref{sec:polsar_models_validation})
                \end{enumerate}
\item The beneficial applications of these
                statistical models have also been demonstrated. Specifically:
                \begin{enumerate}
                \item \label{itm:filter_vicious_circle} The consistent sense of variance
                is shown to help breaking the vicious cycle in the problem of SAR
                speckle filtering: with new statistical test for
                homogeneity and new speckle filters proposed (Sections: \ref{sec:k_mle}, \ref{sec:f_mle}).
                \item \label{itm:log_mse} The consistent sense of subtractive
                distance also helps in the problem of evaluating SAR
                speckle filters. Section \ref{sec:sar_filters_evaluation} proposes the use of the log-MSE to combine the
                evaluation of radiometric preservation and speckle
                suppression power in evaluating SAR speckle filters.
                \item \label{itm:extend_sar_to_polsar} Sections \ref{sec:polsar_models_validation} and \ref{sec:polsar_speckle_filters_evaluation} demonstrate several instances where existing SAR
                processing techniques are extended towards POLSAR data.
                \end{enumerate}
\end{enumerate}

@@

The
                proposed models for POLSAR also bring forward several
                important benefits.
Since
                the models, especially those for discrimination
                measures, can be considered as the multidimensional
                extension of the models for SAR, it makes many existing
                SAR processing techniques extensible towards POLSAR
                data.
The POLSAR determinant ratio, for example, can be considered as
                the extension of the ubiquitous SAR intensity ratio.
This
                thesis also illustrates how the MSE evaluation
                criteria can also be extended from SAR to POLSAR.

From another angle, the theoretical models for POLSAR also offer several benefits.
The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics} \& \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
can be simulated as:
\begin{align}
  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align}
where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
As a by-product of this exact derivation, the current paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.
